mvybdcluster

### 2020-11-22 examples.tex
moved examples to a separate file

 \documentclass{article}
\usepackage{basic}

\title{mvybdcluster}
% \author{Roger Bai, Anne Dranowski, Joel Kamnitzer}
\date{October 2020}

\begin{document}

\maketitle

\section{Background}

The BD Grassmannian. The convolution Grassmannian. Distinguished orbits, slices therein.

\subsection{The case $n=2$ or $1$}

In this case $\Grbd = G(\CC\xT[t^{-1}]/G(\CC[t])$. 
$\Grbd^{\lambda_1,\lambda_2}\to\AA^1$ has 
\begin{itemize}
    \item special fibre $\overline{\Gr^{\lambda_1 + \lambda_2}}$
    \item general fibre $\overline{\Gr^{\lambda_1}}\times\overline{\Gr^{\lambda_2}}$
\end{itemize}
% 
and $S^{\mu_1,\mu_2}_{\mathrm{BD}}\to\AA^1$ has 
\begin{itemize}
    \item special fibre $\overline{S^{\mu_1+\mu_2}}$
    \item general fibre $\overline{S^{\mu_1}}\times \overline{S^{\mu_2}}$
\end{itemize}

Given $s\in \AA^1$ take $t^{\mu_1}(t-s)^{\mu_2} \in \Grbd$ and note that 
\begin{itemize}
    \item[$s\ne 0\Rightarrow$] $S^{\mu_1}\times S^{\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1}(t-s)^{\mu_2}$
    \item[$s = 0\Rightarrow$] $S^{\mu_1+\mu_2} = N(\CC\xT[t^{-1}])t^{\mu_1 + \mu_2}$
\end{itemize}

\jcom{Replace $\CC\xT[t^{-1}]$ by $\CC[t,t^{-1},(t-s)^{-1}]$ everywhere though it won't matter shortly.}

We're interested in
\begin{equation}
\label{eq:topmvy2}
    \tilde\phi_{\mathrm{MVy}}:\Grbd^{\lambda_1,\lambda_2}\cap S^{\mu_1,\mu_2}_{\mathrm{BD}} \to \{\text{some matrices}\}
\end{equation}

\section{Main results}

\begin{claim}
$\widetilde{T_x^a}\to\pi^{-1}(\overline{\Gr^\lambda}\cap\Gr_\mu)$ (this does depend on $b$! we get something like a springer fibre where the action of [what] on either side has eigenvalues a permutation of $b$.)
\end{claim}

\begin{claim}
Let $\cW^\mu_{\rm BD} = G_1\xT[t^{-1}]t^\mu$. Then $S^{\mu_1 + \mu_2}$ is contained in $\cW^\mu_{\rm BD}$ if $\mu$ is dominant. \jcom{And $\mu_1$, $\mu_2$ are dominant also?} \acom{Roger has a proof.}
\end{claim}

\begin{definition}
    Say $\mu_1$ and $\mu_2$ are \new{disjoint} if $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
\end{definition}

\begin{claim}
Let $a = (0,s)$ and suppose $\mu_1$ and $\mu_2$ are disjoint \sout{``transverse''} 
% i.e.\ $(\mu_1)_i\ne 0 \Rightarrow (\mu_2)_i = 0$ and $(\mu_2)_i\ne 0 \Rightarrow (\mu_1)_i = 0$. 
Let $\mu = \mu_1 + \mu_2$. Then $X\in\widetilde{T_x^a}$ is a $\mu\times\mu$ block matrix, with $(\mu_1)_k\times(\mu_1)_k$ diagonal block conjugate to a $(\mu_1)_k$ Jordan block and $(\mu_2)_k\times (\mu_2)_k$ diagonal block conjugate to $(\mu_2)_k$ Jordan block plus $sI$.
\end{claim}

\begin{question}
If $\mu_i$ is not a permutation of $\lambda_i$ and $\lambda_i$ are not ``homogeneous'' how do we proceed? E.g.\ if $\mu_1 = (3,0,2)$, $\mu_2 = (0,2,0)$ and $\lambda_1 = (4,1)$, $\lambda_2 = (2,0,0)$. 
\end{question}

\begin{question}
If $\mu_1$ and $\mu_2$ are not disjoint how do we proceed? E.g.\ if $\mu_1 = (2,2,0)$, $\mu_2 = (1,0,2)$; $\mu_1 = (2,2,1)$, $\mu_2 = (1,0,1)$.
\end{question}

@@

\section{Statements and Proofs of Results}
Define
\[
S_{\mu_1, \mu_2} = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2}
\]
and
\[
W_\mu = G_1 [[t^{-1}]]t^\mu.
\]
Let $|\lambda| = |\lambda_1 + \lambda_2|$ and $|\mu| = |\mu_1 + \mu_2|$.

\begin{lemma}[Proof in Proposition 2.6 of KWWY]
Suppose $\mu$ is dominant. Then 
\[
N((t^{-1})) t^\mu = N_1[[t^{-1}]] t^\mu.
\]
\end{lemma}

\begin{lemma}
For dominant $\mu_1,\mu_2$, we have
\[
S_{\mu_1, \mu_2} \subset W_{\mu_1 + \mu_2}.
\]
\end{lemma}

\begin{proof}
We have
\[
\begin{split}
    S_{\mu_1, \mu_2} & = N((t^{-1}))t^{\mu_1}(t-s)^{\mu_2} \\
     & \subset T_1[[t^{-1}]] N((t^{-1})) t^{\mu_1} (t-s)^{\mu_2} \\
     & = T_1[[t^{-1}]] N_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} \\
     & = B_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & \subset G_1[[t^{-1}]] t^{\mu_1 + \mu_2} \\
     & = W_{\mu_1 + \mu_2}
\end{split}
\]
where $B_1[[t^{-1}]] t^{\mu_1} (t-s)^{\mu_2} = B_1[[t^{-1}]] t^{\mu_1 + \mu_2}$ since 
\[
\frac{t}{t-s} = 
1 + \frac{s}{t} + \frac{s^2}{t^2} + \cdots 
\in B_1[[t^{-1}]].
\]
\end{proof}

Define $Gr^{\lambda_1, \lambda_2} \subset Gr_{BD}$ to be the family with generic fibre $Gr^{\lambda_1} \times Gr^{\lambda_2}$ and 0-fibre $Gr^{\lambda_1 + \lambda_2}$.

Define $\OO_{\lambda_1, \lambda_2}$ to be matrices $X$ of size $|\lambda| \times |\lambda|$ such that 
\[
X|_{E_0} \in \OO_{\lambda_1} \text{ and } (X-sI)|_{E_s} \in \OO_{\lambda_2}.
\]

Let 
\[
\mu = (\mu^{(1)}, \mu^{(2)}, ..., \mu^{(n)}).
\]
Define $\TT_{\mu_1, \mu_2}$ to be $|\mu| \times |\mu|$ matrices $X$ such that $X$ consists of block matrices where the size of the $i$-th diagonal block is $|\mu^{(i)}| \times |\mu^{(i)}|$, for $1\leq i \leq n$.

\begin{theorem}
We have an isomorphism
\[
\overline{Gr^{\lambda_1, \lambda_2}} \cap S_{\mu_1, \mu_2} \cong
\overline{\OO_{\lambda_1, \lambda_2}} \cap \TT_{\mu_1, \mu_2} \cap \n.
\]
\end{theorem}

\begin{proof}
We will prove this similarly to how the usual Mirkovi\'c-Vybornov isomorphism is proven.
\begin{enumerate}[label = Step \arabic*:]
    \item Define a map $\TT_{\mu_1, \mu_2} \cap \cN \rightarrow G_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

    \item If $A \in \TT_{\mu_1,\mu_2} \cap \n$ then $A$ is sent to $(N_-)_1[t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$.

    \item Conversely, given $L \in W_{\mu_1 + \mu_2}$, want to show surjectivity.

\end{enumerate}
\end{proof}
\end{document}

>>>>

% !TeX root = ./main.tex

@@
